### 2016-11-04 section_discussion_subsection_Emission_Physics__.tex
edited section_discussion_subsection_Emission_Physics__.tex

@@

>>>>

Flat luminosity distribution of FRB121102 and overall population

Does local (100 Mpc) population with flat luminosity distribution reproduce observed properties? Imagine also how log-N/log_S cut-offs and scattering biases the intrinsic into the observed distribution (Macquart and Johnston)

Constraints on repetition assuming "red spectrum"

@@

Targeting known FRBs is optimal

Wide, low-sensitivity searches are best way to conduct a blind search
